Performance comparison of Dask and Apache Spark on HPC systems \HL{for Neuroimaging}

### 2022-10-24 latex/paper.tex
[UPDATE] link for github repository.

\HL{
	To minimize the performance difference from implementation decisions, the
	code base of the applications is common for both engines.
	Therefore, the performance observed comes directly from the engine scheduling and
	their APIs.
} The scripts used for our experiments and the results generated are available on
GitHub at: \mbox{\href{https://github.com/mathdugre/paper-big-data-engines}{https://github.com/mathdugre/paper-big-data-engines/}}.

>>>>

\HL{
	To minimize the performance difference from implementation decisions, the
	code base of the applications is common for both engines.
	Therefore, the performance observed comes directly from the engine scheduling and
	their APIs.
} The scripts used for our experiments and the results generated are available on
GitHub at: \mbox{\href{https://github.com/big-data-lab-team/paper-big-data-engines/tree/CPE}{https://github.com/big-data-lab-team/paper-big-data-engines/tree/CPE}}.
